---
title: "DLTs"
author: "Rebecca Silva"
date: "11/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"grade 4 hematologic toxicity, febrile neureopenia, or grade 3 or 4 nonhemotologic tox occurring during the first 2 cycles (28 days) of therapy"

- attribution 3-5
toxicities (from table 2): neuropathy, diarrhea, constipation, nausea, vomiting, anorexia, anemia, neutropenia, thrombocytopenia, fatigue, rash, myalgia, headache, insomnia, edema, dyspnea

explore toxicities : 
```{r}
# patient who started at 1.9 experienced 1 dlt at 1.75 but not in table (constipation)
data_tox %>% 
  filter(patient_id == "9909-N032", course_number %in% c(1, 2), grade == 3, attribution %in% c(3,5)) 
```


ae desscriptions different from ones in table, but in paper authors describe some that would not be attributed to to drug although coded with high attribution. 
```{r}
# all possible toxs: 18 obs - more than in table 
data_tox %>% 
  filter(course_number %in% c(1,2), 
         attribution %in% c(3,5),
         grade %in% c(3,4)) %>% 
  group_by(ae_description) %>% 
  distinct(ae_description, grade, attribution)
  summarise(n= n())


course_number %in% c(1,2), 
         attribution %in% c(3:5),
         grade %in% c(3,4), 
         patient_id != "9909-N032", 
         !(is.na(onset_date))) %>% 
  mutate(ae_description = recode(ae_description, "PERIPHERAL NEUROPATHY SENSORY" = "NEUROPATHY"))

# n total patients: 11
data_tox %>% 
  filter(course_number %in% c(1,2), 
         attribution %in% c(3,5),
         grade %in% c(3,4)) %>% 
  group_by(patient_id) %>% 
  summarise(n_tox= n())
```

```{r}
dlt_data = left_join( data_tox, patient_doses, by = "patient_id") 

#remove unnecessary columns
dlt_data = 
  dlt_data %>% 
  select(-dlt, -protocol, -ctcae_code, -c(serious:outcome))

dlt_data = dlt_data %>% 
  filter(str_detect(ae_description, "NEURO") |
           str_detect(ae_description, "DIARRHEA") |
           str_detect(ae_description, "CONSTIPATION") |
           str_detect(ae_description, "NAUSEA") |
           str_detect(ae_description, "THROMBO") |
           str_detect(ae_description, "FATIGUE")|
           str_detect(ae_description, "ANEMIA"), 
         course_number %in% c(1,2), 
         attribution %in% c(3:5),
         grade %in% c(3,4), 
         patient_id != "9909-N032", 
         !(is.na(onset_date))) %>% 
  mutate(ae_description = recode(ae_description, "PERIPHERAL NEUROPATHY SENSORY" = "NEUROPATHY"))




tab2_data = dlt_data %>% 
  group_by(patient_id, ae_description, dose_level, grade) %>% 
  distinct(patient_id, ae_description, dose_level, grade) %>% # take out if patient had same tox 2x
  group_by(ae_description, dose_level, grade) %>% 
  summarise(n= n()) %>% 
  pivot_wider(
    names_from = dose_level, 
    values_from = n) %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  select(ae_description, grade, `1.2`, `1.75`, `1.9`)

 #seems like some of toxs should be included like lymphopenia bc its a hema?

# will match after... (except for fatigue)
#   - take out data for patient started at 1.9 and moved to 1.75 (for constipation)
#   - add patient who developed neuropathy progression after 28 days
#   - if remove patient w onset data NA for THROMBOCYTOPENIA

test = left_join( data_tox, patient_doses, by = "patient_id")
test %>% filter(dose_level == 1.9, course_number > 2) 
dlt_data %>% filter(dose_level == 1.9, course_number > 2) %>%  
  distinct(patient_id, dose_level)



# this shows that there are other toxicities (grade 4 non-hema, with high attribtuion not labeled in table 2)
# confused because should non-hema be grade 3, 4 - doesnt match table 2 where only grade 3 non-hema, and hema should only be grade 4?
data_tox %>% 
  filter(grade ==4, attribution %in% c(3:5)) 
```

```{r}
# hema: "A hematologic toxicity is defined as neutropenia, anemia, leukopenia, lymphopenia,
# and/or thrombocytopenia."
```


**** 

Defining dlts: 
** not very reproducible because is based on authors table rather than their definition of dlt  
```{r}
patient_dlt = dlt_data %>% mutate(dlt_tox = c(rep(1, nrow(.)))) %>% select(-dose_level)

# add dlts
patient_dlt = left_join(data_tox, patient_dlt)
# add doses
data_tox_dlt = left_join(patient_dlt, patient_doses, by = "patient_id")

# add drug_administration_data 
drug_admin = data_dose %>% select(patient_id, drug_administration_date)
data_tox_dlt = left_join(data_tox_dlt, drug_admin, by = "patient_id")

 
```



***

figure out why missing dlts (none in 1.9) 
```{r}
 test = 
  data_tox %>%
  mutate(ae_description = recode(ae_description, "PERIPHERAL NEUROPATHY SENSORY" = "NEUROPATHY"), 
         ae_description = recode(ae_description, "NEUROPATHY-B/L FEET" = "NEUROPATHY"),
         ae_description = recode(ae_description, "NEUROPATHY (HANDS & FEET)" = "NEUROPATHY"),
         ae_description = recode(ae_description, "INC NEUROPATHY B/L ANKLES-LWR BAK" = "NEUROPATHY"),
         ae_description = recode(ae_description, "PERIPH NEUROPATHY LHAND-ELBOW" = "NEUROPATHY"), 
         ae_description = recode(ae_description, "PERIPH NEUROPATHY LHAND-ELBOW" = "NEUROPATHY"), 
         ae_description = recode(ae_description, "WEAK/FATIGUE" = "FATIGUE"), 
         ae_description = recode(ae_description, "FATIGUE/LETHARGY" = "FATIGUE"),
         ae_description = recode(ae_description, "	THROMBOPENIA" = "THROMBOCYTOPENIA"),) %>% 
  filter(ae_description %in% c("NEUROPATHY","DIARRHEA", "CONSTIPATION", "NAUSEA", "THROMBOCYTOPENIA", "FATIGUE"),
         #patient_id  "9909-N032", 
         !is.na(onset_date), 
         grade %in% c(3,4), 
         course_number %in% c(1,2), 
         attribution %in% c(3:5)) %>% 
  mutate(dlt_tox = c(rep(1, nrow(.)))) %>%  
  distinct(patient_id)

#10 total patients experienced dlt 

 data_tox %>% 
  filter(str_detect(ae_description, "NEUROPATHY") |
           str_detect(ae_description, "DIARRHEA") |
           str_detect(ae_description, "CONSTIPATION") |
           str_detect(ae_description, "NAUSEA") |
           str_detect(ae_description, "THROMBOCYTOPENIA") |
           str_detect(ae_description, "FATIGUE"),
         #patient_id  "9909-N032", 
         #!is.na(onset_date), 
         grade %in% c(3,4), 
         course_number %in% c(1,2), 
         attribution %in% c(3:5)) %>% 
  mutate(dlt_tox = c(rep(1, nrow(.)))) %>%  
  distinct(patient_id)

```

