---
title: "Bortezomib Plots"
author: "Rebecca Silva"
date: "11/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Plot 1
Q: is there a dif btwn drug admin date and course start date 
```{r}
plot_data = 
  data_dose %>% 
  mutate(drug_administration_date = as.Date(drug_administration_date, format="%d-%b-%y")) %>% 
  group_by(patient_id) %>% 
  filter(course_number == 1, 
         drug_administration_date == min(drug_administration_date)) %>% 
  arrange(drug_administration_date)
  
plot_data %>% 
  ggplot(aes(x = drug_administration_date, y = dose_level)) + 
  geom_point(aes(shape = 4)) +
  scale_shape_identity() +
  scale_y_continuous(
    breaks = c(0.25, 0.80, 1.0, 1.20, 1.45, 1.90), 
    labels = c("0.25", "0.80", "1.0", "1.20", "1.45", "1.90")) +
  labs(
    x = "Time", 
    y = "Dose Level"
  )
```

# Plot 2

# defining DLT" - in his code, not the same categories ie "BLOOD AND LYMPHATIC SYSTEM DISORDERS - OTHER, SPECIFY" not there for grade 3 or 4 
"grade 4 hematologic toxicity, febrile neureopenia, or grade 3 or 4 nonhemotologic tox occurring during the first 2 cycles (28 days) of therapy"

"A hematologic toxicity is defined as neutropenia, anemia, leukopenia, lymphopenia,
and/or thrombocytopenia."

def: Neutrophils, Platelets, Hemoglobin, Lymphocytes (total), CD4 count, Febrile neutropenia


```{r}
data_dlt = 
  data_tox %>% 
  filter(course_number < 3, attribution > 2) %>% 
  mutate(hematologic = ifelse(ae_description %in% c("ANEMIA","LEUKOPENIA", "LYMPHOPENIA", "NEUTROPENIA", "THROMBOCYTOPENIA"), 1, 0), 
         non_hematologic = ifelse(hematologic == 0, 1, 0), 
         dlt_hema = ifelse(hematologic ==1 & grade == 4, 1, 0),
         dlt_nonhema =  ifelse(non_hematologic == 1 & grade >=3 , 1, 0),
         dlt = ifelse(dlt_hema| dlt_nonhema, 1, 0))

# non-hemo def must be wrong because it inlcudes everything that is not hemo, therefore all ae grade >2 is dlt?
# all ae
adverse_events = 
  data_tox %>%  filter(as.numeric(grade) > 2 ) %>% group_by(ae_description) %>%  summarise(n())

# his code - incorrect
GetHematologicCategories <- function(){
  tox <- read.delim("/Users/daniel/NonDData/Data/NCI/merged.recoded.toxicities.txt", stringsAsFactors=F)
  hematologic <- c("WHITE BLOOD CELL DECREASED", "PLATELET COUNT DECREASED",
                   "BLOOD AND LYMPHATIC SYSTEM DISORDERS - OTHER, SPECIFY",
                   "NEUTROPHIL COUNT DECREASED", "LYMPHOCYTE COUNT DECREASED", 
                   "ANEMIA", "FEBRILE NEUTROPENIA", 
                   "DISSEMINATED INTRAVASCULAR COAGULATION")
  hematologic <- c(hematologic, grep("HEMORRHAGE", unique(tox$FINAL.DESCR), value=T))
  return(hematologic)
}

```

## plot2 data
```{r}
# all entry dates
entry_date = 
  data_dose %>% 
  mutate(date = as.Date(drug_administration_date, format="%d-%b-%y"), 
         dlt = c(rep(0,nrow(.)))) %>% # since filtered out no dlt entries for paitent w dlt (still want entry pt as no dlt)
  distinct(patient_id, date, dlt) %>% 
  arrange(date) %>%
  group_by(patient_id) %>% 
  mutate(earliest_date = min_rank(date)) %>% 
  filter(earliest_date == 1) %>% 
  select(-earliest_date)

# patients w no dlts ever 
no_dlt_patients = 
  data_dlt %>% 
  group_by(patient_id) %>% 
  summarise(dlt_sum= sum(dlt)) %>% 
  mutate(dlt_ever = ifelse(dlt_sum == 0, 0, 1)) %>% 
  filter(dlt_ever == 0) %>% 
  pull(patient_id) # make vector of patient_ids

# end = 2 weeks after entry if no dlt 
end_date_no_dlt = 
  entry_date %>% 
  filter(patient_id %in% no_dlt_patients) %>% 
  mutate(date = bizdays::offset(date, 28)) %>% 
  select(patient_id, date, dlt)

end_dates_dlt = 
  data_dlt %>% 
  filter(!(patient_id %in% no_dlt_patients), dlt == 1) %>% # if paitent has dlt want to remove rows with dlt = 0 
  mutate(date = as.Date(onset_date, format="%d-%b-%y")) %>% 
  select(patient_id, date, dlt)  

dates_all = 
  bind_rows(end_date_no_dlt, end_dates_dlt, entry_date) 

# add dose_level and ids
id_column = 
  dates_all %>% 
  arrange(date) %>%
  group_by(patient_id) %>% 
  mutate(earliest_date = min_rank(date)) %>% 
  distinct(patient_id, earliest_date) %>% 
  filter(earliest_date == 1) %>% 
  tibble::rowid_to_column("id_by_entry") %>% 
  select(id_by_entry, patient_id)

dose_level_column = 
  data_dose %>% 
  select(patient_id, dose_level) %>% # some paatient got more than one dose -- choosing smaller dose
  group_by(patient_id) %>% 
  mutate(earliest_date = min_rank(dose_level)) %>%
  distinct(patient_id, dose_level, earliest_date) %>% 
  filter(earliest_date == 1) %>% 
  select(-earliest_date)

merge1 = left_join(dates_all, id_column, by = "patient_id") 
final = left_join(merge1, dose_level_column, by = "patient_id")

```

# plots 
```{r}
final %>% 
  ggplot(aes(x = date, y = id_by_entry)) +
  geom_point(aes(shape = as.factor(dlt), color = as.factor(dlt))) +
  theme(legend.position = "") +
  geom_line(aes(group = id_by_entry)) +
  scale_shape_manual(values = c(20, 4)) +
  scale_color_manual(values = c("black", "red")) +
  geom_text(data = text_labels, 
            aes(x = as.Date(x), y = y, label= text), size=2.5, hjust = -.5) +
  labs(
    x= "Date", 
    y = "id")



final %>% 
  ggplot(aes(x = date, y = dose_level)) +
  geom_point(aes(group = id_by_entry, shape = as.factor(dlt))) +
  theme(legend.position = "") +
  geom_line(aes(group = id_by_entry)) +
  scale_shape_manual(values = c(20, 4)) +
  scale_y_continuous(
    breaks = c(0.25, 0.80, 1.0, 1.20, 1.45, 1.75, 1.90), 
    labels = c("0.25", "0.80", "1.0", "1.20", "1.45", "1.75", "1.90"))

text_labels = 
  final %>% 
  group_by(patient_id) %>% 
  summarise(
    x = max(date), 
    y = max(id_by_entry), 
    text = max(dose_level))
  
```



