---
title: "3+3"
author: "Rebecca Silva"
date: "10/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 3+3 Design: 
+ start w 3 patients at dose level X
-- if no DLT : proceed to dose level X + 1 with 3 new patients
-- if 1 DLT : add 3 to dose level X
-- if 2 or more DLTs: stop dose escalation, proceed to dose level X - 1 with 3 patients or if X = 1 stop 
-- if 1 or more of additional patients have DLT and only 3 evaluated at dose level X - 1, add 3 to X-1. If not, trial ends. 

# CRM model 

Copied code: - change norm to unif and skeleton to p_0
addition file from https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/s12874-018-0638-z#MOESM1

https://uvatrapps.shinyapps.io/crmb/
https://uvatrapps.shinyapps.io/crmb/
http://faculty.virginia.edu/model-based_dose-finding/ - might have something on simulations (code)

Number of doses; 
  Dose range needs to allow for accurate estimation of MTD. Spacing allow important. 


Dose-toxicity model; F(B, d) where B is parameter, and d is vector of dose labels
* the dose label for the ith dose is di such that pi = F(β*, di)
# model describes prob of DLT as given dose - will use Power model 

# Givens:
```{r}
# number of doses
n_levels = 6
dose = c(10, 20, 40, 80, 120, 160)
# set probability of experiencing DLT (TTL) btwn 20% - 35%
TTL<-0.30 
# prior belief is that dose level 4 is the MTD
mtd<-4 

# initial prior DLT probs
p_0 = c(0.02, 0.065, 0.10, 0.20, 0.33, 0.65) # dose toxicity skeleton (expected DLT probabilities at each dose level- spec. by clinicians)

# prior distribution ‘beta’
beta = runif(n = 1e6) 
# mean prior 
prior_beta = mean(beta)

# dose label for the ith dose is di such that pi = F(β*, di) (B* = prior)
dose_label = p_0^(1/exp(prior_beta)) 

# list of prior distributions for probability of DLT per dose level
prob_dist = lapply(1:n_levels, function(x) (dose_label[x])^(exp(prior_beta))) #(same as prior_beta but for future p's as well)
```
 
Inference:


Data from patients in the trial are used to update the prior distribution (prob_dist) on the model parameter(s), which then gives a posterior distribution for the model parameter(s) and therefore posterior beliefs for the probability of DLT at each dose. These posterior probabilities are used to make dose escalation decisions: 
** the dose level for next patient is the dose associated with the posterior toxicity prob closest to the target, p (.3)

Starting dose of CRM can be the prior estimate of MTD (4)

 We may adapt the dose for the next patient or cohort by estimating the probability of DLT for each dose level, whether from a likelihood-based or Bayesian approach, and then choosing the dose level using a specified decision rule. 
 
```{r}
# power function
f = function(i , param){ # how to incorporate x? x = fn of dose x = {(x(1), y1),...(x(j), yj)}
  return(p[i]^exp(param)) # returns yi (response outcome for ith patient)
}

# likelyhood fn
lik_index = 1
lik = function( x, beta){ # y[j] is jth patient response/outcome (I would make up y[j] ie 1 or 0)
  for( r in 1:j){
  product = lik_index*(f(r, beta))^y[r]*(1-f(r, beta))^(1-y[r])
  lik_index = product
  }
}
# before integration, find min and max of param - i used percentiles 
param_min = quantile(beta, .025)
param_max = quantile(beta, 0.975)
# bayes formula for post
post_dist = lik(x, param)* prior_beta/ (integrate(lik(x, param)* prior_beta, lower = param_min, upper = param_max))

post_mean = mean(post_dist)

# actualized values of toxic prob at each dose level di (new p)
# make list for i dose levels, j patients 
for(j in 1:num_patients){
  for (i in 1:n_levels){
  p[i] = f(i, post_mean)
  }
}


num_patients = 3 # num of patients
```
*** left off above 
 
 
 
Decision rules; choosing the dose with an estimated probability of DLT closest to the TTL. 
Theorectical: minarg(distance btwn actualized prob and p= F(x(i), B))
 
```{r}
# decision rule = choose dose with an estimated prob of DLT closest to the TTL 
p_closest = which.min(abs(p[num_patients]-TTL))
dose_index = match(p_closest, p[num_patients])

# give next patient dose= dose_index 
x[num_patients + 1] = dose_label[dose_index]
```
 
*** still need to specify responses and create loop / first test our with one patient 

Sample size and cohort size;
```{r}
n = 24
```

Safety modifications;
Stopping rules.
Examples of stopping rules: 
a fixed number of patients have been consecutively dosed at one dose level [49]; the estimated probability of all dose levels having a DLT rate above (or below) the TTL is at least 90% [57, 58]; the width of the likelihood-based confidence interval or Bayesian credible interval for the MTD reaches a particular level [10]; the probability that the next m patients to be dosed in the trial will be given the same dose level, regardless of DLT outcomes observed, exceeds some level (e.g., 90%) [10, 56, 59]; or any combination of these [54]. 
```{r}
# stopping rule = stop when say 5 patients have been consecutively dosed at one dose level 

```

Scenarios to simulate: 
The dose-toxicity scenarios used in the simulation study should include: scenarios where each dose is in fact the MTD; two extreme scenarios, in which the lowest dose is above the MTD and the highest dose is below the MTD; and any others that clinicians believe are plausible. 

Questions: 
- how does the main function incorporate the function of x's if the pwr fn p^exp(B) does not include x? 
- the credibility interval to find minBeta/theta and max_param
- where does 1.34 for var of B come from (its in all models as default and says "normal prior")





