---
title: "Untitled"
author: "Rebecca Silva"
date: "12/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dfcrm)
```

Note: Rmd uses enviroment from "define_dlt.Rmd"


# Get arguments from data 
```{r}
n = nrow(data_dose %>% distinct(patient_id))
doses = c(0.25, 0.8, 1, 1.2, 1.45, 1.75, 1.9)

# vec of pt doses in order 
dose_level = 
  left_join(patient_doses, start_date, by = "patient_id") %>%  
  arrange(start_date) %>% 
  pull(dose_level)

# get dose number from dose level - matches dose_level to doses 
dose_number = match(dose_level, doses)

#vector of pt outcomes 
tox = left_join(dlt_data, id_column, by = "patient_id") %>% 
  arrange(id_by_entry) %>% 
  distinct(patient_id, dlt_patient) %>% 
  pull(dlt_patient)
```


```{r}
# get prior function 

# arguments: 
halfwidth = 0.05
nu = 4 # prior guess of mtd 
target = 0.30 # prob experience DLT 
nlevel = length(doses)

# DLT prob for each dose level 
prior = getprior(halfwidth, target, nu, nlevel, model = "empiric")
```

# run crm
```{r}
# using full data - recommended next dose # = 5 (1.45)
x = crm(prior, target, tox, dose_number, n = n)

crm(prior, target, tox, dose_number, n = n, include = 1:10)


# find recommended next dose after each patient 
output = vector("list", length = n )
dose_recommended = c()
for ( i in 1:n){ 
  output[[i]] = dfcrm::crm(prior, target, tox, dose_number, 
             n = n, 
             include = 1:i)
  dose_recommended = c(dose_recommended, output[[i]]$mtd)
}

# convert dose_recommended (number) back to dose_level to compare
dose_level_rec = doses[dose_recommended]

dose_level_rec = prepend(dose_level_rec, 1.45) # since rec is for next pt need to add 
dose_level_rec = dose_level_rec[-41] # only need 39 recs because 40 pts

# compare dose_level_rec to true dose_level
df = tibble(
  dose_rec = dose_level_rec,
  dose = dose_level
)

ggplot(df, aes(x = dose, y = dose_rec)) + 
  geom_point()  
 #geom_abline(0, 1, color= "red")

```


# make plot of recommended doses 
```{r}
names(dose_level_rec) = c(1:length(dose_level_rec))
rec = as.data.frame(cbind(id_column %>% pull(id_by_entry), dose_level_rec))
colnames(rec) = c("id_by_entry", "dose_level_rec")
with_id = left_join(id_column, rec, by = "id_by_entry")

crm_dlt_data = left_join(dlt_data, with_id, by = "patient_id")

crm_dlt_data %>%
  distinct(patient_id, dose_level_rec, dlt_patient, start_date) %>% 
  ggplot(aes(x = start_date, y = dose_level_rec)) + 
  geom_point(aes(shape = 4, color = as.factor(dlt_patient)), position = position_jitter(w = 0, h = .01)) +
  scale_shape_identity() +
  scale_color_manual(values = c("black", "red")) +
  scale_y_continuous(
    breaks = c(0.25, 0.80, 1.0, 1.20, 1.45, 1.75, 1.90), 
    labels = c("0.25", "0.80", "1.0", "1.20", "1.45", "1.75", "1.90")) +
  labs(
    x = "Time", 
    y = "Dose Level"
  ) +
  theme(legend.position = "none") 
```

These recommended doses use true data for every "include" so not realistic since dlts occured on different doses than what is shown. SO instead, we next want to simulate the crm. 

Phats will be based on percentage that experienced dlt at each dose. And then we modify to make it monotonic. 

```{r}
# get initial p-hats 
true_phat_df = 
  dlt_data %>% 
  distinct(patient_id, dlt_patient, dose_level) %>% 
  group_by(dose_level) %>% 
  summarize(p_hat = sum(dlt_patient)/n()) 

#%>% 
 # filter( dose_level != 1.9) # take out 1.9 for more steep curve 


# graph 
true_phat_df %>% 
  ggplot(aes( x = dose_level, y = p_hat)) +
  geom_point()

# fit quadratic?
# second order polynomial:
x = true_phat_df %>% pull(dose_level)
y = true_phat_df %>% pull(p_hat)
p = plot(x,y)
fit = lm(y ~ poly(x, 2, raw = TRUE))
lines(dose_level, predict(fit, data.frame(x= dose_level)),col="red")
  
```
Second order model: p_hat = -0.008697  - 0.060469(dose_level) + 0.144603(dose_level)^2 

NOW: (without 1.9): 

```{r}
# get estimated p_hats
est_phat = vector("list", length = length(doses) )
index = 1
for (i in doses){
  est_phat[index] = -0.008697 - 0.060469*i + 0.144603*i^2 
  index = index + 1
}
est_phat= unlist(est_phat)
est_phat[1] = 0.001 # prob cant be negative


# try isotonic regression (monotonically increasing fn)
fit = isoreg(x, y)
plot(fit)
est_phat_iso = fit$yf
```

Q: confused if doing 3+3 desgin with crm or 
```{r}
# use crmsim for cohorts of size 3
# PI = true tox probabilities (but ive modified too) 
crmsim(PI = est_phat_iso, prior, target = .25, n = 39, x0 = 1, nsim = 100, mcohort = 3, restrict = TRUE,
count = TRUE, method = "bayes", model = "empiric",
scale = sqrt(1.34), seed = 1009)

# order: 3, 6, 6, 9, 6, 0 - 

## too conservative with second order polynomial? (est_phat). mtd is 5 (1.45) selected 50% of time, 1.75 selected 30% of time (100 sims). target = .25

# all conservative for isotonic regression. mtd is 5 (1.45) chosed .48% and 6 (1.75) chosen .38% of the time 
```


```{r}
# compare to crm mtd with full data 
crm(prior, target = .25, unname(tox), dose_number, n = n) # mtd = 5
```

Table data:
```{r}
# do sim and crm with table data 
table_df = 
  tibble(
  dose_level = doses, 
  n_dlts = c(0, 0, 0, 1, 0, 5, 4), 
  true_prob_dlt = c(0, 0, 0, 1/6, 0, 5/13, 7/13)
  )

fit_table = isoreg(table_df$true_prob_dlt)
est_phat_tbl = fit_table$yf

# simulation
crmsim(PI = est_phat_tbl, prior, target = .25, n = 39, x0 = 1, nsim = 100, mcohort = 3, restrict = TRUE,
count = TRUE, method = "bayes", model = "empiric",
scale = sqrt(1.34), seed = 1009) # choses dose number 6 (1.75), 63% 

# compare
crm(prior, target = .25, unname(tox), dose_number, n = n) # mtd = 5

```



```{r}
# use 3+3 design and see where dose assignment differs

# check structures 
dose_level; tox


output = vector("list", length = n )
dose_recommended = c()
for ( i in 1:13){ 
  output[[i]] = dfcrm::crm(prior, target = .25, unname(tox), dose_number, 
             n = n, 
             include = 1:3*i) 
  dose_recommended = c(dose_recommended, output[[i]]$mtd)
}

crm(prior, target, unname(tox), dose_number, 
             n = n, 
             include = 1:19)

# .25 (3) --> .8 (3) --> 1.0 (3) ---> 1.2(6) ---> 1.45 (4) ---> 1.75(3) * differs here because jumps to 1.9 and not 1.75 and also does 4 on 1.45 but included this 

```

```{r}
# crmsim does this for us
n_dlt = c()
for (i in 1:7){
  bin_sim = rbinom(3, size = 100, est_phat[i])
  n_dlt[i] = sum(bin_sim)
}
```

Starting titecrm: 
go to tite_crm.rmd 
